---
title: "UK Student Loan Debt Calculator"
author: "Conrado Eiroa-Solans & Diego Ramos"
output: html_document
---
Here is some custom code to calculate how long it will take you to repay your debt if you studied in the UK and took a loan from the government. All you have to do is introduce the amount of debt you undertook for your undergrad/postgrad studies, your expected salary in the future, and how much of your salary at any given moment you'd like to put towards your repayment. 

Input these values in the following lines: 
  Undergrad debt: line 21
  Grad debt: line 22
  Expected salary: line 29
  Repayment rate undergrad: line 47
  Repayment rate postgrad: line 53


```{r}
undergrad_debt = vector(mode = "integer", length = 25)
graduate_debt = vector(mode = "integer", length = 25)

#YOUR INPUT
undergrad_debt[1] = 33260.94
graduate_debt[1] = 10382.71

#Set up data
years = 1:25 #years after graduating.Here, we're looking at 25 years into the future. 
th_income1 = 26575 # income threshold 1 (as per UK guidelines in 2020; surpassed = pay more fees)
th_income2 = 47835 # income threshold 2 (when surpassed, you pay even higher fees)
postgrad_interest = rep(1.056, 25) #again, as of 2020
salary = c(0, (rep(25000,4)), (rep(30000,5)), (rep(50000,5)), (rep(75000,10))) #this is kind of arbitrary, but the idea is that you will earn 25k for ~4 years, 30 for 5 etc. Can be updated. 


#Interest to pay per year depending on salary 
undergrad_interest = vector(mode = "integer", length = 25)
for (i in 1:length(undergrad_interest)) {
  if (salary[i] <= th_income1){         
  undergrad_interest[i] = 1.026 
}  else if (salary[i] > th_income1 && salary[i] <= th_income2){ 
    undergrad_interest[i] = 1.026 + (( (salary[i]-th_income1) / (th_income2-th_income1) ) *0.03)
}  else {
    undergrad_interest[i]= 1.056 }}
undergrad_interest = as.numeric(format(round(undergrad_interest, 3)))

#Yearly repayment amount based on salary (currently the minimum)
repayment_ug = vector(mode = "integer", length = 25)
for (i in 1:length(repayment_ug)) {
  if (salary[i] >= th_income1){
  repayment_ug[i] = salary[i] * 0.09 #undergrad (9% min)
  }}

repayment_pg = vector(mode = "integer", length = 25)
for (i in 1:length(repayment_pg)) {
  if (salary[i] >= th_income1){
  repayment_pg[i] = salary[i] * 0.06  #graduate (6% min)
  }}

#Graduate debt (original + annual interest)

for (i in 2:length(graduate_debt)) {
  if(((graduate_debt[[i-1]]) * postgrad_interest[i]) - (repayment_pg[i]) > 0){
  graduate_debt[i] = (graduate_debt[[i-1]] *postgrad_interest) - (repayment_pg[i])
  } else 
  graduate_debt[i] = 0
}

#Undergraduate debt (original + annual interest)
for (i in 2:length(undergrad_debt)) {
  if (((undergrad_debt[[i-1]]) * undergrad_interest[i]) - (repayment_ug[i]) > 0){
    undergrad_debt[i] = (undergrad_debt[[i-1]] * undergrad_interest) - (repayment_ug[i])}
    else 
    undergrad_debt[i] = 0
  }

#Make pretty + Add total debt
undergrad_debt = as.numeric(format(round(undergrad_debt,2)))
graduate_debt = as.numeric(format(round(graduate_debt,2))) 
total_debt = undergrad_debt + graduate_debt


#Make sure all money goes to repayment and there are no over-payments last year
for(i in 2:length(repayment_ug)){
  if(undergrad_debt[[i-1]]<repayment_ug[i]){
    repayment_ug[i] = undergrad_debt[[i-1]]
  }}

for(i in 2:length(repayment_pg)){
  if(graduate_debt[[i-1]]<repayment_pg[i]){
    repayment_pg[i] = graduate_debt[[i-1]]
  }}

#Create cumulative payments
cumulative_payments = rep(0,25)
for(i in 2:length(repayment_pg)){
  cumulative_payments[i] = cumulative_payments[[i-1]] + repayment_pg[i] + repayment_ug[i]
}


#Create dataframe
dataframe = cbind(years,undergrad_debt, graduate_debt, salary,repayment_ug, repayment_pg, undergrad_interest, postgrad_interest, total_debt, cumulative_payments)


```


```{r}
#Plot!
par(mar = c(7, 5, 3, 5))
grand_total = cumulative_payments[25]
percent_increase = round(((grand_total / (undergrad_debt[1] + graduate_debt[1])) -1) * 100, 2)

plot(dataframe[1:25, 2], type="l",col="blue", ylab = "Debt", xlab = "Years", main = "How long until ultimate freedom?", ylim = c(0,50000))

mysubtitle = paste0("Received: £",(undergrad_debt[1] + graduate_debt[1]),"    Repaid:  £", grand_total,".   That's a ", percent_increase, "% increase.")
mtext(side=1, line=5,  mysubtitle)

lines(dataframe[1:25, 3],col="red")
legend("topright", c("Undergrad", "Grad"),
       col = c("blue", "red"), lty = c(1, 1))


```


